### 2017-11-27 Chapter2/related.tex
Latest on 26/11/2017
Latest on 27/11/2017

    The UCB-Improved  stated in algorithm \ref{alg:ucbi}, proposed in \citet{auer2010ucb}, is a round-based variant of UCB1. An algorithm is \textit{round-based} if it pulls all the arms equal number of times in each round and then eliminates one or more arms that it deems to be sub-optimal. Note, that in this algorithm the confidence interval term is $\sqrt{\dfrac{\log{( T\epsilon_{m}^{2})}}{2 n_{m}}}$ which is constant in the $m$-th round as $n_m$ is fixed for that round and all arms are being pulled an equal number of times in each round. This is unlike UCB1 algorithm where the confidence interval term depends on $n_i$ which is a random variable. Also, note that in UCB-Improved the knowledge of horizon is required before-hand to calculate the confidence intervals whereas no such input is required for UCB1.

@@

    In the later work of \citet{audibert2009minimax}, the authors propose the MOSS algorithm and showed that the worst case gap-independent regret bound of MOSS is $O\left( \sqrt{KT} \right)$ which improves upon UCB1 by a factor of order $\sqrt{\log T}$. However, the gap-dependent regret of MOSS is $O\left( \frac{K^{2}\log\left(T\Delta^{2}/K\right)}{\Delta}\right)$ and in certain regimes, this can be worse than even UCB1 (see \citet{audibert2009minimax,lattimore2015optimally}).

    Recently in \citet{lattimore2015optimally}, the authors showed that  the algorithm OCUCB achieves order-optimal gap-dependent regret bound of $O\left(\sum_{i=2}^{K}\frac{\log\left(T/H_i\right)}{\Delta_i}\right)$ where $H_i=\sum_{j=1}^{K}\min\left\lbrace \frac{1}{\Delta_i^2},\frac{1}{\Delta_j^2}\right\rbrace$, and a gap-independent regret bound of $O\left( \sqrt{KT}\right)$. This is the best known gap-dependent and gap-independent regret bounds in the stochastic MAB framework. However, unlike our proposed EUCBV algorithm (in chapter \ref{chap:EUCBV}), OCUCB does not take into account the variance of the arms; as a result, empirically  we find  that our algorithm outperforms OCUCB in all the environments considered.

@@

    In contrast to the above work, the UCBV \citep{audibert2009exploration} algorithm utilizes variance estimates to compute the confidence intervals for each arm. In UCBV the confidence interval term is given by $\sqrt{\dfrac{2\hat{v}_i\log (t)}{s_i}} + \dfrac{3\log (t)}{3}$ where $\hat{v}_i$ denotes the empirical variance of the arm $i$. Hence, the confidence interval makes sure that the arms whose variances are high are pulled more often to get a better estimates of their $\hat{r}_i$.

@@

\begin{table}[!ht]
\caption{Confidence interval of different algorithms}
\label{tab:conf-comp}
\begin{center}
\begin{tabular}{|p{5em}|p{10em}|p{4em}|p{12em}|}
\hline
Algorithm  &  Confidence interval & Horizon as input & Remarks \\
\hline
\hline
UCB1        & $\sqrt{\dfrac{2\log (t)}{n_i}}$ & No & Loose confidence interval leading to high regret upper bounds.\\%\midrule
\hline
\hline
UCBV        & $\sqrt{\dfrac{2\hat{v}_i\log (t)}{s_i}} + \dfrac{3\log (t)}{2}$ & No & Confidence interval uses variance estimation.\\
\hline
\hline
UCB-Imp 		& $\sqrt{\dfrac{\log{( T\epsilon_{m}^{2})}}{2 n_{m}}}$ & Yes & Same confidence interval for all arms in a particular round.\\%\midrule
\hline
\hline
MOSS	     	& $\sqrt{\dfrac{\max\lbrace 0,\log(\frac{T}{K n_i})\rbrace}{n_i}}$ & Yes & Confidence interval is based on dividing the horizon uniformly for $K$ arms.\\%\midrule
\hline
\hline
OCUCB     	& $\sqrt{\dfrac{2\log(\frac{2T}{t})}{n_i}}$ & Yes & Tightest confidence interval leading to order-optimal regret bounds.\\\midrule
\end{tabular}
\end{center}
%\vspace*{-2em}
\end{table}

>>>>

    The UCB-Improved  stated in algorithm \ref{alg:ucbi}, proposed in \citet{auer2010ucb}, is a round-based variant of UCB1. An algorithm is \textit{round-based} if it pulls all the arms equal number of times in each round and then eliminates one or more arms that it deems to be sub-optimal. Note, that in this algorithm the confidence interval term is $\sqrt{\dfrac{\log{( T\epsilon_{m}^{2})}}{2 n_{m}}}$ which is constant in the $m$-th round as $n_m$ is fixed for that round and all arms are being pulled an equal number of times in each round. This is unlike UCB1 algorithm where the confidence interval term depends on $n_i$ which is a random variable. Also, note that in UCB-Improved the knowledge of horizon is required before-hand to calculate the confidence intervals whereas no such input is required for UCB1. An illustrative flowchart depicting the main steps is given in Figure \ref{fig:ucbimp}.

\begin{figure}[!th]
\includegraphics[scale=0.45]{Chapter2/img/Ucb-Imp.png}
\caption{Flowchart of UCB-Improved}
\label{fig:ucbimp}
\end{figure}

@@

    In the later work of \citet{audibert2009minimax}, the authors propose the MOSS algorithm (see algorithm \ref{alg:moss}) and showed that the worst case gap-independent regret bound of MOSS is $O\left( \sqrt{KT} \right)$ which improves upon UCB1 by a factor of order $\sqrt{\log T}$. However, the gap-dependent regret of MOSS is $O\left( \frac{K^{2}\log\left(T\Delta^{2}/K\right)}{\Delta}\right)$ and in certain regimes, this can be worse than even UCB1 (see \citet{audibert2009minimax,lattimore2015optimally}).

\subsubsection{OCUCB Algorithm}

\begin{algorithm}[!th]
\caption{OCUCB}
\label{alg:ocucb}
\begin{algorithmic}[1]
\State \textbf{Input:} Time horizon $T$, $K$ number of arms with unknown parameters of reward distribution, exploration parameter $\alpha$ and $\psi$
\State Pull each arm once
 \For{$t=K+1,..., T$}
\State Pull the arm such that $\argmax_{i\in \A}\bigg\lbrace\hat{r}_{i} + \sqrt{\dfrac{\alpha\log(\psi\frac{T}{t})}{n_i}}\bigg\rbrace$
\State $t:=t+1 $
 \EndFor
\end{algorithmic}
\end{algorithm}

Recently in \citet{lattimore2015optimally}, the authors showed that the algorithm Optimally Confident UCB (OCUCB) (see algorithm \ref{alg:ocucb}) achieves order-optimal gap-dependent regret bound of $O\left(\sum_{i=2}^{K}\frac{\log\left(T/H_i\right)}{\Delta_i}\right)$ where $H_i=\sum_{j=1}^{K}\min\left\lbrace \frac{1}{\Delta_i^2},\frac{1}{\Delta_j^2}\right\rbrace$, and a gap-independent regret bound of $O\left( \sqrt{KT}\right)$. This is the best known gap-dependent and gap-independent regret bounds in the stochastic MAB framework. However, unlike our proposed EUCBV algorithm (in chapter \ref{chap:EUCBV}), OCUCB does not take into account the variance of the arms; as a result, empirically  we find  that our algorithm outperforms OCUCB in all the environments considered.

@@

    In contrast to the above work, the UCB-Variance (UCBV) algorithm in \citet{audibert2009exploration} utilizes variance estimates to compute the confidence intervals for each arm. In UCBV (see algorithm \ref{alg:ucbv}) the confidence interval term is given by $\sqrt{\dfrac{2\hat{v}_i\log (t)}{s_i}} + \dfrac{3\log (t)}{3}$ where $\hat{v}_i$ denotes the empirical variance of the arm $i$. Hence, the confidence interval makes sure that the arms whose variances are high are pulled more often to get a better estimates of their $\hat{r}_i$.

@@

\begin{table}[!ht]
\caption{Confidence interval of different algorithms}
\label{tab:conf-comp}
\begin{center}
\begin{tabular}{|p{5em}|p{10em}|p{4em}|p{12em}|}
\hline
Algorithm  &  Confidence interval & Horizon as input & Remarks \\
\hline
\hline
UCB1        & $\sqrt{\dfrac{2\log (t)}{n_i}}$ & No & Loose confidence interval leading to high regret upper bounds.\\%\midrule
\hline
\hline
UCBV        & $\sqrt{\dfrac{2\hat{v}_i\log (t)}{s_i}} + \dfrac{3\log (t)}{2}$ & No & Confidence interval uses variance estimation.\\
\hline
\hline
UCB-Imp 		& $\sqrt{\dfrac{\log{( T\epsilon_{m}^{2})}}{2 n_{m}}}$ & Yes & Same confidence interval for all arms in a particular round.\\%\midrule
\hline
\hline
MOSS	     	& $\sqrt{\dfrac{\max\lbrace 0,\log(\frac{T}{K n_i})\rbrace}{n_i}}$ & Yes & Confidence interval is based on dividing the horizon uniformly for $K$ arms.\\%\midrule
\hline
\hline
OCUCB     	& $\sqrt{\dfrac{2\log(\frac{2T}{t})}{n_i}}$ & Yes & Tightest confidence interval with exploration parameter $\alpha=2$, $\psi=2$ leading to order-optimal regret bounds.\\\midrule
\end{tabular}
\end{center}
%\vspace*{-2em}
\end{table}

### 2017-11-27 Chapter3/Conclusion.tex
Latest on 27/11/2017

In this chapter, we studied the EUCBV algorithm which takes into account the empirical variance of the arms and employs aggressive exploration parameters in conjunction with non-uniform arm selection (as opposed to UCB-Improved) to eliminate sub-optimal arms. Our theoretical analysis conclusively established that EUCBV exhibits an order-optimal gap-independent regret bound of $O\left(\sqrt{KT}\right)$. Empirically, we show that EUCBV performs superbly across diverse experimental settings and outperforms most of the bandit algorithms in a  stochastic MAB setup. Our experiments show that EUCBV is extremely stable for larger horizons and performs consistently well across different types of distributions. One avenue for future work is to remove the constraint of $T\geq K^{2.4}$ required for EUCBV to reach the order optimal regret bound. Another future direction is to come up with an anytime version of EUCBV. An anytime algorithm does not need the horizon $T$ as an input parameter.

>>>>

In this chapter, we studied the EUCBV algorithm which takes into account the empirical variance of the arms and employs aggressive exploration parameters in conjunction with non-uniform arm selection (as opposed to UCB-Improved) to eliminate sub-optimal arms. Our theoretical analysis conclusively established that EUCBV exhibits an order-optimal gap-independent regret bound of $O\left(\sqrt{KT}\right)$. Empirically, we show that EUCBV performs superbly across diverse experimental settings and outperforms most of the bandit algorithms in an SMAB setup. Our experiments showed that EUCBV is extremely stable for large horizons and performs consistently well across different types of distributions.

### 2017-11-27 Chapter3/proofTheorem.tex
Latest on 27/11/2017

%\subsection{Lemma 1}
%\label{sec:proofTheorem:Lemma1}
We first present a few technical lemmas that is required  to prove the result in Theorem \ref{Result:Theorem:1}.

@@

\begin{lemma}
\label{proofTheorem:Lemma:2}
If $T\geq K^{2.4}$, $\psi=\frac{T}{ K^2}$, $\rho =\frac{1}{2}$, $m_i = min\lbrace m|\sqrt{4\epsilon_{m} } < \frac{\Delta_i}{4} \rbrace $ and $c_{i} =\sqrt{\frac{\rho (\hat{v}_i + 2)\log (\psi T\epsilon_{m_{i}})}{4 z_i}}$, then,
%\begin{align*}
\center $c_{i} < \frac{\Delta_i}{4}$.
%\end{align*}
\end{lemma}

\begin{lemma}
\label{proofTheorem:Lemma:3}
If $m_i = min\lbrace m|\sqrt{4\epsilon_{m} } < \frac{\Delta_i}{4} \rbrace $,  $c_{i} = \sqrt{\frac{\rho (\hat{v}_i + 2) \log (\psi T\epsilon_{m_{i}})}{4 z_{i}}}$ and $n_{m_i} = \frac{\log{(\psi T\epsilon_{m_{i}})}}{2\epsilon_{m_{i}}}$ then we can show that,
\begin{align*}
\mathbb{P}(\hat{r}_{i}> r_{i} + c_{i})\le \dfrac{2}{(\psi  T\epsilon_{m_{i}})^{\frac{3\rho}{2}}}.
\end{align*}
\end{lemma}

@@

\noindent
\textbf{Case $(b1)$ (\textit{${*}\in B_{m_{i}}$ and each ${i}\in \A^{'}$ is  eliminated on or before $m_{i}$ }): } Since we are eliminating a sub-optimal arm ${i}$ on or before round $m_{i}$, it is pulled no longer than, 
 \begin{align*}
 z_{i} < \bigg\lceil\dfrac{\log{(\psi T\epsilon_{m_{i}}^{2})}}{2\epsilon_{m_{i}}}\bigg\rceil
 \end{align*}
%\hspace*{4em}
%%$, since $\sqrt{\rho_{a}\epsilon_{m_{i}}}\leq\dfrac{\Delta_{i}}{2}
So, the total contribution of ${i}$  till round $m_{i}$ is given by, 
\begin{align*}
&\Delta_{i}\bigg\lceil\dfrac{\log{(\psi T\epsilon_{m_{i}}^{2})}}{2\epsilon_{m_{i}}}\bigg\rceil
\overset{(a)}{\leq}    \Delta_{i}\bigg\lceil\dfrac{\log{(\psi T(\dfrac{\Delta_{i}}{16 \times 256})^{4})}}{2(\dfrac{\Delta_{i}}{4\sqrt{4}})^{2}}\bigg\rceil \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&\leq   \Delta_{i}\bigg(1+\dfrac{32\log{(\psi T(\dfrac{\Delta_{i}^{4}}{16384})}}{\Delta_{i}^{2}}\bigg)
\leq \Delta_{i}\bigg(1+\dfrac{32\log{(\psi T\Delta_{i}^{4})}}{\Delta_{i}^{2}}\bigg) .
\end{align*}

>>>>

%\subsection{Lemma 1}
%\label{sec:proofTheorem:Lemma1}
We first present a few technical lemmas that are required  to prove the result in Theorem \ref{Result:Theorem:1}.

@@

\begin{lemma}
\label{proofTheorem:Lemma:2}
If $T\geq K^{2.4}$, $\psi=\frac{T}{ K^2}$, $\rho =\frac{1}{2}$, $m_i = min\lbrace m|\sqrt{4\epsilon_{m} } < \frac{\Delta_i}{4} \rbrace $ and $c_{i} =\sqrt{\frac{\rho (\hat{v}_i + 2)\log (\psi T\epsilon_{m_{i}})}{4 z_i}}$, then,
\begin{align*}
 c_{i} < \frac{\Delta_i}{4}.
\end{align*}
\end{lemma}

\begin{lemma}
\label{proofTheorem:Lemma:3}
If $m_i = min\lbrace m|\sqrt{4\epsilon_{m} } < \frac{\Delta_i}{4} \rbrace $,  $c_{i} = \sqrt{\frac{\rho (\hat{v}_i + 2) \log (\psi T\epsilon_{m_{i}})}{4 z_{i}}}$ and $n_{m_i} = \frac{\log{(\psi T\epsilon_{m_{i}})}}{2\epsilon_{m_{i}}}$ then we can show that in the $m_i$-th round,
\begin{align*}
\mathbb{P}(\hat{r}_{i}> r_{i} + c_{i})\le \dfrac{2}{(\psi  T\epsilon_{m_{i}})^{\frac{3\rho}{2}}}.
\end{align*}
\end{lemma}

@@

\noindent
\textbf{Case $(b1)$ (\textit{${*}\in B_{m_{i}}$ and each ${i}\in \A^{'}$ is  eliminated on or before $m_{i}$ }): } Since we are eliminating a sub-optimal arm ${i}$ on or before round $m_{i}$, it is pulled no longer than, 
 \begin{align*}
 z_{i} < \bigg\lceil\dfrac{\log{(\psi T\epsilon_{m_{i}}^{2})}}{2\epsilon_{m_{i}}}\bigg\rceil
 \end{align*}
%\hspace*{4em}
%%$, since $\sqrt{\rho_{a}\epsilon_{m_{i}}}\leq\dfrac{\Delta_{i}}{2}
So, the total contribution of ${i}$ until round $m_{i}$ is given by, 
\begin{align*}
&\Delta_{i}\bigg\lceil\dfrac{\log{(\psi T\epsilon_{m_{i}}^{2})}}{2\epsilon_{m_{i}}}\bigg\rceil
\overset{(a)}{\leq}    \Delta_{i}\bigg\lceil\dfrac{\log{(\psi T(\dfrac{\Delta_{i}}{16 \times 256})^{4})}}{2(\dfrac{\Delta_{i}}{4\sqrt{4}})^{2}}\bigg\rceil \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&\leq   \Delta_{i}\bigg(1+\dfrac{32\log{(\psi T(\dfrac{\Delta_{i}^{4}}{16384})}}{\Delta_{i}^{2}}\bigg)
\leq \Delta_{i}\bigg(1+\dfrac{32\log{(\psi T\Delta_{i}^{4})}}{\Delta_{i}^{2}}\bigg) .
\end{align*}

### 2017-11-27 Chapter4/prevRes.tex
Latest on 27/11/2017

\subsection{Unified Setting}
Apart from these two settings some unified approaches has also been suggested in \citet{gabillon2012best} which proposes the algorithms UGapEb and UGapEc which can work in both the above two settings.

>>>>

\subsection{Unified Setting}
Apart from these two settings some unified approaches has also been suggested in \citet{gabillon2012best} which proposes the algorithms UGapEb and UGapEc which can work in both the fixed budget setting and fixed confidence  setting.

### 2017-11-27 Chapter6/intro.tex
Latest on 27/11/2017

In this paper, we consider the piece-wise stochastic multi-armed bandit problem, an interesting variation of the stochastic multi-armed bandit problem in sequential decision making. In this setting,  a learning algorithm is provided with a set of decisions (or arms) with reward distributions unknown to the learner. The learning proceeds in an iterative fashion, where in each round, the algorithm chooses an arm and receives a stochastic reward that is drawn from a distribution specific to the arm selected. There exist a finite number of changepoints such that the reward distribution of arms changes at those changepoints. Given the goal of maximizing the cumulative reward, the learner faces the \textit{exploration-exploitation-changepoint} dilemma, i.e., in each round should the algorithm select the arm which has the highest observed reward so far (\textit{exploitation}), or should the algorithm choose a new arm to gain more knowledge of the expected reward of the arms and thereby avert a sub-optimal greedy decision (\textit{exploration}) and finally keep track of the \textit{changepoints}.

>>>>

In this chapter, we consider the piece-wise stochastic multi-armed bandit problem, an interesting variation of the stochastic multi-armed bandit (SMAB) problem in sequential decision making. In this setting,  a learning algorithm is provided with a set of decisions (or arms) with reward distributions unknown to the learner. The learning proceeds in an iterative fashion, where in each round, the algorithm chooses an arm and receives a stochastic reward that is drawn from a distribution specific to the arm selected. There exist a finite number of changepoints such that the reward distribution of arms changes at those changepoints. Given the goal of maximizing the cumulative reward, the learner faces the \textit{exploration-exploitation-changepoint} dilemma, i.e., in each round should the algorithm select the arm which has the highest observed reward so far (\textit{exploitation}), or should the algorithm choose a new arm to gain more knowledge of the expected reward of the arms and thereby avert a sub-optimal greedy decision (\textit{exploration}) and finally keep track of the \textit{changepoints}.

### 2017-11-27 Chapter6/notations.tex
Latest on 27/11/2017

In this paper, $T$ denotes the time horizon. $\A$ denotes the set of arms with individual arm is denoted by $i$ such that $i=1,\ldots, K$. We assume that the total number of arms is constant throughout the time horizon and $|\A|=K$. In this setting each arm has a piece-wise stationary distribution associated with it. Let $c_0,c_1,c_2,\ldots,c_G$ denotes $G$ such changepoints which belong to the set $\G$ and $|\G|=G$. Here, $c_0$ is a virtual changepoint which starts at $t=1$. 
We denote each of the \textit{non-overlapping reward generating processes} as $\rho_{c_j}$, $j\in\mathbb{N}$. Note that the learner does not know these changepoints or the total number of changepoints in the environment.

@@

	The distribution associated with individual arm $i$ is denoted by $D_{i,\rho_{c_j:c_{j+1}}}$ for the segment $\rho_{c_j:c_{j+1}}$ whereas the reward drawn from that distribution for the $t$-th time instant is denoted by $X_{i,t}$. We assume all rewards are bounded in $[0,1]$. $n_{i,t_0:t_p}$ denotes the number of times arm $i$ has been pulled from $t_0$ to $t_p$ timesteps. $\mu_{i,t_{c_j:c_{j+1}}}$ denotes the expected mean of the reward distribution $D_{i,\rho_{c_j:c_{j+1}}}$ and $\hat{\mu}_{i,t_0:t_p}$ denotes the sample mean for the arm $i$ from $t_0$ to $t_p$ timesteps.

@@

\begin{align*}
t_{c_j}& = \min\left\lbrace t\in[1,T],\forall i\in\A : \mu_{i,t_{c_{j-1}:c_j}} \neq \mu_{i,t_{c_{j}:c_{j+1}}}   \right\rbrace\\
%%%%%%%%%%%%%%%%%%%%%%%%%%
%&= \min\left\lbrace t\in[1,T],\forall i\in\A: \Delta^{chg}_{i,c_j} \geq \Delta_0 \right\rbrace
\end{align*}

@@

\begin{definition}
\label{Def:chg-gap}
We define the changepoint gap at $t_{c_j}$ for an arm $i\in\A$ between the segments $\rho_{c_{j-1}:c_j}$ and $\rho_{c_j:c_{j+1}}$ as,
\begin{align*}
\Delta^{chg}_{i,c_j}=|\mu_{i,t_{c_{j-1}:c_j}}-\mu_{i,t_{c_j:c_{j+1}}}|.
\end{align*}
\end{definition}

@@

\begin{definition}
\label{Def:opt-gap}
We define the optimality gap $\Delta^{opt}_{i,c_j}$ for an arm $i_{t'}\neq i^*_{t'},\forall t'\in[t_{c_{j-1}},t_{c_j}]$ as,
\begin{align*}
\Delta^{opt}_{i,c_j}= \mu_{i^*,t_{c_{j-1}:c_j}}-\mu_{i,t_{c_{j-1}:c_j}}.
\end{align*}
\end{definition}

Also, recall from Definition \ref{Def:chg-gap} that the changepoint gap $\Delta^{chg}_{i,c_j}=|\mu_{i,t_{c_{j-1}:c_j}}-\mu_{i,t_{c_j:c_{j+1}}}|$.

>>>>

Again, to benefit the reader we state the notations used in this chapter. $T$ denotes the time horizon. $\A$ denotes the set of arms with individual arm is denoted by $i$ such that $i=1,\ldots, K$. We assume that the total number of arms is constant throughout the time horizon and $|\A|=K$. In this setting each arm has a piece-wise stationary distribution associated with it. Let $c_0,c_1,c_2,\ldots,c_G$ denotes $G$ such changepoints which belong to the set $\G$ and $|\G|=G$. Here, $c_0$ is a virtual changepoint which starts at $t=1$. 
We denote each of the \textit{non-overlapping reward generating processes} as $\rho_{c_j}$, $j\in\mathbb{N}$. Note that the learner does not know these changepoints or the total number of changepoints in the environment.

@@

	The distribution associated with individual arm $i$ is denoted by $D_{i,\rho_{c_j:c_{j+1}}}$ for the segment $\rho_{c_j:c_{j+1}}$ whereas the reward drawn from that distribution for the $t$-th time instant is denoted by $X_{i,t}$. We assume all rewards are bounded in $[0,1]$. $n_{i,t_0:t_p}$ denotes the number of times arm $i$ has been pulled from $t_0$ to $t_p$ timesteps. $r_{i,t_{c_j:c_{j+1}}}$ denotes the expected mean of the reward distribution $D_{i,\rho_{c_j:c_{j+1}}}$ and $\hat{r}_{i,t_0:t_p}$ denotes the sample mean for the arm $i$ from $t_0$ to $t_p$ timesteps.

@@

\begin{align*}
t_{c_j}& = \min\left\lbrace t\in[1,T],\forall i\in\A : r_{i,t_{c_{j-1}:c_j}} \neq r_{i,t_{c_{j}:c_{j+1}}}   \right\rbrace\\
%%%%%%%%%%%%%%%%%%%%%%%%%%
%&= \min\left\lbrace t\in[1,T],\forall i\in\A: \Delta^{chg}_{i,c_j} \geq \Delta_0 \right\rbrace
\end{align*}

@@

\begin{definition}
\label{Def:chg-gap}
We define the changepoint gap at $t_{c_j}$ for an arm $i\in\A$ between the segments $\rho_{c_{j-1}:c_j}$ and $\rho_{c_j:c_{j+1}}$ as,
\begin{align*}
\Delta^{chg}_{i,c_j}=|r_{i,t_{c_{j-1}:c_j}}-r_{i,t_{c_j:c_{j+1}}}|.
\end{align*}
\end{definition}

@@

\begin{definition}
\label{Def:opt-gap}
We define the optimality gap $\Delta^{opt}_{i,c_j}$ for an arm $i_{t'}\neq i^*_{t'},\forall t'\in[t_{c_{j-1}},t_{c_j}]$ as,
\begin{align*}
\Delta^{opt}_{i,c_j}= r_{i^*,t_{c_{j-1}:c_j}}-r_{i,t_{c_{j-1}:c_j}}.
\end{align*}
\end{definition}

Also, recall from Definition \ref{Def:chg-gap} that the changepoint gap $\Delta^{chg}_{i,c_j}=|r_{i,t_{c_{j-1}:c_j}}-r_{i,t_{c_j:c_{j+1}}}|$.

### 2017-11-27 Chapter6/probDef.tex
Latest on 27/11/2017

Given the exploration-exploitation-changepoint dilemma, the objective of the learner in the piecewise-stochastic bandit problem is to minimize the cumulative regret until time $t$, which is defined as follows:
\begin{align*}
R_{t}=\sum_{t'=1}^t\mu_{i^*_{t'}} - \sum_{t'=1}^t\mu_{I_t'}
%R_{t}=\sum_{t'=1}^t\mu_{i^*_{t'}} - \sum_{i=1}^K \left(\mu_{i}n_{i_{t'}\neq i^*_{t'},\forall t'=1:t}\right),
\end{align*}
where $t$ is the number of rounds, $\mu_{i^*_{t'}}$ is the optimal arm at the $t'$ timestep and $\mu_{I_{t'}}$ is the arm chosen by the learner at the $t'$ timestep. Let $n_{i_{t'}\neq i^*_{t'},\forall t'=1:t}$ is the number of times the learner has chosen arm $i$ up to round $t$ when it was not the optimal arm $i^*_{t'}$. The expected regret of an algorithm after $t$ rounds can be written as,

\begin{align*}
\E[R_{t}]&= \E\left[\sum_{t'=1}^t\mu_{i^*_{t'}} - \sum_{t'=1}^t\mu_{I_t}\right]\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&=\sum_{i\neq i^*}^K\left(\mu_{i^*} - \mu_i\right) \E[n_{i_{t'}\neq i^*_{t'},\forall t'=1:t}] \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&\overset{(a)}{=}\sum_{i\neq i^*}^K\sum_{j=1}^{G}\Delta^{opt}_{i,c_j}\E[n_{i_{t'}\neq i^*_{t'},\forall t'=t_{c_{j-1}}:t_{c_j}}]
\end{align*}
where $(a)$ is obtained from assumption \ref{assm:chg-gap} and $\Delta^{opt}_{i,c_j}$ is defined as in Definition \ref{Def:opt-gap}.

>>>>

Given the exploration-exploitation-changepoint dilemma, the objective of the learner in the piecewise-stochastic bandit problem is to minimize the cumulative regret until time $t$, which is defined as follows:
\begin{align*}
R_{t}=\sum_{t'=1}^t r_{i^*_{t'}} - \sum_{t'=1}^t r_{I_t'}
%R_{t}=\sum_{t'=1}^t r_{i^*_{t'}} - \sum_{i=1}^K \left(r_{i}n_{i_{t'}\neq i^*_{t'},\forall t'=1:t}\right),
\end{align*}
where $t$ is the number of rounds, $r_{i^*_{t'}}$ is the optimal arm at the $t'$ timestep and $r_{I_{t'}}$ is the arm chosen by the learner at the $t'$ timestep. Let $n_{i_{t'}\neq i^*_{t'},\forall t'=1:t}$ is the number of times the learner has chosen arm $i$ up to round $t$ when it was not the optimal arm $i^*_{t'}$. The expected regret of an algorithm after $t$ rounds can be written as,

\begin{align*}
\E[R_{t}]&= \E\left[\sum_{t'=1}^t r_{i^*_{t'}} - \sum_{t'=1}^t\mu_{\mathbb{I}_t'}\right]\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&=\sum_{i\neq i^*}^K\left(r_{i^*} - r_i\right) \E[n_{i_{t'}\neq i^*_{t'},\forall t'=1:t}] \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&\overset{(a)}{=}\sum_{i\neq i^*}^K\sum_{j=1}^{G}\Delta^{opt}_{i,c_j}\E[n_{i_{t',c_j}\neq i^*_{t',c_j},\forall t'=t_{c_{j-1}}:t_{c_j}}]
\end{align*}
where $(a)$ is obtained from assumption \ref{assm:chg-gap} and $\Delta^{opt}_{i,c_j}$ is defined as in Definition \ref{Def:opt-gap}.
